On the specific recursive structure of iterated parametricity

### 2025-09-28 paper/paper.tex
paper: typeset (frame|painting|restrf)type, adjust font-sz
paper: swap sections; first section reminder
paper: change convention n -> n+p in tables
paper: \cohc -> \cohp

\newcommand{\frametype}{\ensuremath{\mathsf{frametype}}}
\newcommand{\paintingtype}{\ensuremath{\mathsf{paintingtype}}}
\newcommand{\restrftype}{\ensuremath{\mathsf{restrftype}}}

@@

% These are renewed in tables, but let's define them now for in-document
% typesetting
\newcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
\newcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
\newcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
\newcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
\newcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
\newcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
\newcommandx{\cohf}{\coh{frame}[][][][][][][][]}
\newcommandx{\cohl}{\coh{layer}[][][][][][][][]}
\newcommandx{\cohc}{\coh{painting}[][][][][][][][]}
\newcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
\newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}

@@

@@

        Schematically, using dotted arrows for dependencies in
        the type and plain arrows for dependencies in the definition, this
        gives the following dependencies for $p\leq n$ fixed:
        \begin{center}
          \begin{tikzcd}
            \framep[n][0,...,p] \arrow[d] \arrow[ddr]\\
            \painting[n-1][0,...,p-1] \arrow[d, dotted] \\
            \framep[n-1][0,...,p-1] &
            \restrf[n][0,...,p-1] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[0,...,p-1]$}"', near start, shift right=2mm, hook']\\
          \end{tikzcd}
        \end{center}

@@

        $$
          \begin{array}{llcl}
            \frametype^{n,[0,...,p]}  &                                                     & :      & Type_{l+1}                                                               \\
            \frametype^{n,[]}         &                                                     & \defeq & unit                                                                     \\
            \frametype^{n,[0,...,p]}  &                                                     & \defeq & \frametype^{n,[0,...,p-1]} \times Type_l                               \\
            \\
            \paintingtype^{n,[0,...,p]} & (\framep[n][0,...,p]:\frametype^{n,[0,...,p]}) & :      & Type_{l+1}                                                               \\
            \paintingtype^{n,[]}        & \star                                               & \defeq & unit                                                                     \\
            \paintingtype^{n,[0,...,p]} & (\framep[n][0,...,p])                            & \defeq & \paintingtype^{n,[0,...,p-1]}(\framep[n][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
          \end{array}
        $$

@@

@@

                        \framep[n-1][0,...,p-1]:\frametype^{n-1,[0,...,p-1]}                               \\
                        \painting[n-1][0,...,p-1]:\paintingtype^{n-1,[0,...,p-1]}(\framep[n-1][0,...,p-1]) \\
                        \restrf[n][0,...,p-1]:\restrftype^{n,[0,...,p-1]}

@@

                      \end{array}\right) : \frametype^{n-1,[0,...,p]}

@@

            \restrftype^{n,[0,...,p-1]}                            &

@@

                        \framep[n-1][0,...,p-1]:\frametype^{n-1,[0,...,p-1]}                               \\
                        \painting[n-1][0,...,p-1]:\paintingtype^{n-1,[0,...,p-1]}(\framep[n-1][0,...,p-1]) \\

@@

            \restrftype^{n,[]}                                     &

@@

            \restrftype^{n,[0,...,p]}                              &

@@

              \quad:\restrftype^{n,[0,...,p-1]}

@@

            \frametype^{n,[p,...,n]}  &                                                     & :      & Type_{l+1}                                                               \\
            \frametype^{n,[]}         &                                                     & \defeq & unit                                                                     \\
            \frametype^{n,[p,...,n]}  &                                                     & \defeq & Type_l \times \frametype^{n,[p+1,...,n-1]}                               \\

@@

            \paintingtype^{n,[p,...,n]} & (\framep[n][p,...,n]:\frametype^{n,[p,...,n]}) & :      & Type_{l+1}                                                               \\
            \paintingtype^{n,[]}        & \star                                               & \defeq & unit                                                                     \\
            \paintingtype^{n,[p,...,n]}_{p<n} & (\framep[n][p,...,n])                            & \defeq & (\framep[n][p] \rightarrow Type_l) \times \paintingtype^{n,[p+1,...,n]}(\framep[n][p+1,...,n]) \\

@@

            \restrftype^{n,[p,...,n]} &

@@

                        \framep[n-1][0,...,p-1]:\frametype^{n-1,[0,...,p-1]}                               \\
                        \painting[n-1][0,...,p-1]:\paintingtype^{n-1,[0,...,p-1]}(\framep[n-1][0,...,p-1]) \\
                        \framep[n-1][p,...,n-1]:\frametype^{n-1,[p,...,n-1]}                                     \\
                        \painting[n-1][p,...,n-1]:\paintingtype^{n-1,[p,...,n-1]}(\framep[n-1][p,...,n-1])           \\
                        \restrf[n][0,...,p-1]:\restrftype^{n,[0,...,p-1]}

@@

            \restrftype^{n,[p,...,n-1]} &

@@

                                \rightarrow \framep[n-1][p]\\

@@

                                \restrftype^{n,[p+1,...,n]}

@@

        This allows to define $\painting[n][p]$ formally:
        $$
          \begin{array}{llcl}
            \painting[n][p]                                     &
            \multicolumn{3}{l}{
              \left(\begin{array}{l}
                        \framep[n-1][0,...,p-1]:\frametype^{n-1,[0,...,p-1]}                               \\
                        \painting[n-1][0,...,p-1]:\paintingtype^{n-1,[0,...,p-1]}(\framep[n-1][0,...,p-1]) \\
                        \framep[n-1][p,...,n-1]:\frametype^{n-1,[p,...,n-1]}                                     \\
                        \painting[n-1][p,...,n-1]:\paintingtype^{n-1,[p,...,n-1]}(\framep[n-1][p,...,n-1])           \\
                        \restrf[n][0,...,p-1]:\restrftype^{n,[0,...,p-1]}
                                \left(\begin{array}{l}
                                    \framep[n-1][0,...,p-1]  \\
                                    \painting[n-1][0,...,p-1] \\
                                  \end{array}\right) \\
                        \restrf[n][p,...,n-1]:\restrftype^{n,[p,...,n-1]}
                                \left(\begin{array}{l}
                                    \framep[n-1][0,...,p-1]  \\
                                    \painting[n-1][0,...,p-1] \\
                                    \framep[n-1][p,...,n-2]  \\
                                    \painting[n-1][p,...,n-2] \\
                                    \restrf[n][0,...,p-1] \\
                                  \end{array}\right) \\
                        E:\framep[n-1][n-1]\rightarrow Type_l\\
                      \end{array}\right) : \framep[n-1][n-1]\rightarrow Type_l
            }    \\
            \painting[n][n]                                           &
            \left(\begin{array}{l}
                      \framep[n-1][0,...,n-1] \\
                      \painting[n-1][0,...,n-1] \\
                      \star \\
                      \star \\
                      \restrp[n][0,...,n-1] \\
                      \star \\
                      E \\
                    \end{array}\right)                                     & \defeq & E \\
            \painting[n][p](p<n)                                   &
                                \left(\begin{array}{l}
                                    \framep[n-1][0,...,p-1]  \\
                                    \painting[n-1][0,...,p-1] \\
                                    \framep[n-1][p,...,n-1]  \\
                                    \painting[n-1][p,...,n-1] \\
                                    \restrf[n][0,...,p-1] \\
                                    \restrf[n][p,...,n-1] \\
                                    E \\
                                  \end{array}\right) & \defeq & d \mapsto
            \left(\begin{array}{l}
              \Sigma l:(\Pi q\leq n.\,\Pi \omega.\
                      \painting[n-1][0,...,p](\restrf[n][p](d))). \\
                      \painting[n][p+1,...,n-1]
                      \left(\begin{array}{l}
                                    \framep[n-1][0,...,p]  \\
                                    \painting[n-1][0,...,p] \\
                                    \framep[n-1][p+1,...,n-1]  \\
                                    \painting[n-1][p+1,...,n-1] \\
                                    \restrf[n][0,...,p] \\
                                    \restrf[n][p+1,...,n-1] \\
                                    E \\
                        \end{array}\right)(d,l) \\
                    \end{array}\right)                    \\
          \end{array}
          $$

@@

\section{Our construction}
% Abbreviated tables in this section
%
% The rule for implicit arguments for each table:
% show 1 explicit in first two parts
% show E + 1 explicit in the third part
\appendmask[bonak]{layer}[D]
\appendmask[bonak]{painting}[D]
\appendmask[bonak]{restrframe}[D]
\appendmask[bonak]{restrlayer}[D, d]
\appendmask[bonak]{restrpainting}[D, d]
\appendmask[bonak]{cohframe}[D]
\appendmask[bonak]{cohlayer}[D, d]
\appendmask[bonak]{cohpainting}[D, d]

% Coherence conditions for frame, layer, and painting
% Keep only ε, ω; n, p; proposition on n and p
\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][][][][][#9]}

Notably, the definition of $\restrl$ relies on an equality expressing the commutation of the composition of two $\restrf$. The proof of this commutation is worth being made explicit, which we do in table~\ref{tab:coh} using proof-term notations. The proof requires an induction on the dimension and on the structure of $\framep$, $\layer$, and $\painting$. This is what $\cohf$ does using auxiliary proofs $\cohl$ and $\cohc$. Even though it looks independent of the definitions from the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions. More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be defined in one go by induction on $p$. Also, each of $\painting$, $\restrp$, and $\cohc$ is built by induction from $p$ to $n$. The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but the converse dependency is only on lower $n$, so this is well-founded. Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations. The exact way this mutual recursion is eventually formalized is explained in section~\ref{sec:wf}.

% Truncated sets, otherwise referred to as X
% Drop the universe letter for the third and fourth tables
\renewcommandx{\Xto}[3][3]{\X[][<#2][#3]}
\renewcommandx{\Xcomp}[3][3]{\X[][=#2][#3]}
\renewcommandx{\Xfrom}[3][3]{\X[][\geq#2][#3]}

% Frame, layer, and painting
% Drop all arguments for coh table; they're not present in coind table.
\renewcommandx{\framep}[5][1,2,3,4,5]{\prim{frame}[][][][][#5]}
\renewcommandx{\layer}[5][1,2,3,4,5]{\prim{layer}[][][][][#5]}
\renewcommandx{\painting}[5][1,2,3,4,5]{\prim{painting}[][][][][#5]}

% Hack to remove , in \cohf
\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}

% Coherence conditions for frame, layer, and painting
\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohc}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}

>>>>

@@

% These are renewed in tables, but let's define them now for in-document
% typesetting
\newcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
\newcommandx{\frametype}[2][1,2]{\prim{frametype}[][#1][#2][][]}
\newcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
\newcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
\newcommandx{\paintingtype}[2][1,2]{\prim{paintingtype}[][#1][#2][][]}
\newcommandx{\restrftype}[2][1,2]{\prim{restrftype}[][#1][#2][][]}
\newcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
\newcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
\newcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}
\newcommandx{\cohf}{\coh{frame}[][][][][][][][]}
\newcommandx{\cohl}{\coh{layer}[][][][][][][][]}
\newcommandx{\cohp}{\coh{painting}[][][][][][][][]}
\newcommandx{\coht}{\cohtwo{frame}[][][][][][][][]}
\newcommandx{\fullframe}[1][1]{\prim{fullframe}[][#1][][][]}

@@

\section{Reminder of our construction}
% Abbreviated tables in this section
%
% The rule for implicit arguments for each table:
% show 1 explicit in first two parts
% show E + 1 explicit in the third part
\appendmask[bonak]{layer}[D]
\appendmask[bonak]{painting}[D]
\appendmask[bonak]{restrframe}[D]
\appendmask[bonak]{restrlayer}[D, d]
\appendmask[bonak]{restrpainting}[D, d]
\appendmask[bonak]{cohframe}[D]
\appendmask[bonak]{cohlayer}[D, d]
\appendmask[bonak]{cohpainting}[D, d]

% Coherence conditions for frame, layer, and painting
% Keep only ε, ω; n, p; proposition on n and p
\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][][][][][#9]}
\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][][][][][#9]}
\renewcommandx{\cohp}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][][][][][#9]}

Notably, the definition of $\restrl$ relies on an equality expressing the commutation of the composition of two $\restrf$. The proof of this commutation is worth being made explicit, which we do in table~\ref{tab:coh} using proof-term notations. The proof requires an induction on the dimension and on the structure of $\framep$, $\layer$, and $\painting$. This is what $\cohf$ does using auxiliary proofs $\cohl$ and $\cohp$. Even though it looks independent of the definitions from the other tables, $\cohf$ has to be proved mutually with the definitions of $\framep$, $\layer$, $\painting$, and their corresponding restrictions. More precisely, for a fixed $n$, the block of $\framep$, $\restrf$, and $\cohf$ has to be defined in one go by induction on $p$. Also, each of $\painting$, $\restrp$, and $\cohp$ is built by induction from $p$ to $n$. The $\painting$ block at $n$ relies on the $\framep$ block at $n$, but the converse dependency is only on lower $n$, so this is well-founded. Note that $\layer$, $\restrl$ and $\cohl$ are just abbreviations. The exact way this mutual recursion is eventually formalized is explained in section~\ref{sec:wf}.

% Coherence conditions for frame, layer, and painting
\renewcommandx{\cohf}[9][1,2,3,4,5,6,7,8,9]{\coh{frame}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohl}[9][1,2,3,4,5,6,7,8,9]{\coh{layer}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\cohp}[9][1,2,3,4,5,6,7,8,9]{\coh{painting}[][#2][#3][#4][#5][#6,#7][#8][#9]}
\renewcommandx{\coht}[9][1,2,3,4,5,6,7,8,9]{\cohtwo{frame}[][#2][#3][#4][#5][#6][#7,#8][#9]}

\renewcommandx{\framep}[2][1,2]{\prim{frame}[][#1][#2][][]}
\renewcommandx{\layer}[2][1,2]{\prim{layer}[][#1][#2][][]}
\renewcommandx{\painting}[2][1,2]{\prim{painting}[][#1][#2][][]}
\renewcommandx{\restrf}[4][1,2,3,4]{\restr{frame}[][#3][#4][#1][#2][][]}
\renewcommandx{\restrl}[4][1,2,3,4]{\restr{layer}[][#3][#4][#1][#2][][]}
\renewcommandx{\restrp}[4][1,2,3,4]{\restr{painting}[][#3][#4][#1][#2][][]}

@@

        Schematically, using dotted arrows for dependencies in
        the type and plain arrows for dependencies in the definition, this
        gives the following dependencies for $p\leq n$ fixed:
        \begin{center}
          \fontsize{7.2}{9}\selectfont
          \begin{tikzcd}
            \framep[n][0,...,p] \arrow[d] \arrow[ddr]\\
            \painting[n-1][0,...,p-1] \arrow[d, dotted] \\
            \framep[n-1][0,...,p-1] &
            \restrf[n][0,...,p-1] \arrow[l, dotted] \arrow[uul, dotted, "\mbox{$[0,...,p-1]$}"', near start, shift right=2mm, hook']\\
          \end{tikzcd}
        \end{center}

@@

        $$
          \fontsize{7.2}{9}\selectfont
          \begin{array}{llcl}
            \frametype[n][0,...,p]    &                                              & :      & Type_{l+1}                                                                                   \\
            \frametype[n][]           &                                              & \defeq & unit                                                                                         \\
            \frametype[n][0,...,p]    &                                              & \defeq & \frametype[n][0,...,p-1] \times Type_l                                                       \\
            \\
            \paintingtype[n][0,...,p] & (\framep[n][0,...,p]:\frametype[n][0,...,p]) & :      & Type_{l+1}                                                                                   \\
            \paintingtype[n][]        & \star                                        & \defeq & unit                                                                                         \\
            \paintingtype[n][0,...,p] & (\framep[n][0,...,p])                        & \defeq & \paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \times (\framep[n][p] \rightarrow Type_l) \\
          \end{array}
        $$

@@

          \fontsize{7.2}{9}\selectfont

@@

                        \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                        \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
                        \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]

@@

                      \end{array}\right) : \frametype[n-1][0,...,p]

@@

            \restrftype[n][0,...,p-1]  &

@@

                        \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                        \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\

@@

            \restrftype[n][]           &

@@

            \restrftype[n][0,...,p]    &

@@

              \quad:\restrftype[n][0,...,p-1]

@@

            \frametype[n][p,...,n]         &                                              & :      & Type_{l+1}                                                                                   \\
            \frametype[n][]                &                                              & \defeq & unit                                                                                         \\
            \frametype[n][p,...,n]         &                                              & \defeq & Type_l \times \frametype[n][p+1,...,n-1]                                                     \\

@@

            \paintingtype[n][p,...,n]      & (\framep[n][p,...,n]:\frametype[n][p,...,n]) & :      & Type_{l+1}                                                                                   \\
            \paintingtype[n][]             & \star                                        & \defeq & unit                                                                                         \\
            \paintingtype[n][p,...,n](p<n) & (\framep[n][p,...,n])                        & \defeq & (\framep[n][p] \rightarrow Type_l) \times \paintingtype[n][p+1,...,n](\framep[n][p+1,...,n]) \\

@@

            \restrftype[n][p,...,n]        &

@@

                        \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                        \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
                        \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
                        \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
                        \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]

@@

            \restrftype[n][p,...,n-1]      &

@@

              \rightarrow \framep[n-1][p] \\

@@

              \restrftype[n][p+1,...,n]

@@

        This allows to define $\painting[n][p]$ formally:
        $$
          \fontsize{7.2}{9}\selectfont
          \begin{array}{llcl}
            \painting[n][p]              &
            \multicolumn{3}{l}{
              \left(\begin{array}{l}
                        \framep[n-1][0,...,p-1]:\frametype[n-1][0,...,p-1]                               \\
                        \painting[n-1][0,...,p-1]:\paintingtype[n-1][0,...,p-1](\framep[n-1][0,...,p-1]) \\
                        \framep[n-1][p,...,n-1]:\frametype[n-1][p,...,n-1]                               \\
                        \painting[n-1][p,...,n-1]:\paintingtype[n-1][p,...,n-1](\framep[n-1][p,...,n-1]) \\
                        \restrf[n][0,...,p-1]:\restrftype[n][0,...,p-1]
                        \left(\begin{array}{l}
                            \framep[n-1][0,...,p-1]   \\
                            \painting[n-1][0,...,p-1] \\
                          \end{array}\right)                                                  \\
                        \restrf[n][p,...,n-1]:\restrftype[n][p,...,n-1]
                        \left(\begin{array}{l}
                            \framep[n-1][0,...,p-1]   \\
                            \painting[n-1][0,...,p-1] \\
                            \framep[n-1][p,...,n-2]   \\
                            \painting[n-1][p,...,n-2] \\
                            \restrf[n][0,...,p-1]     \\
                          \end{array}\right)                                                  \\
                        E:\framep[n-1][n-1]\rightarrow Type_l                                            \\
                      \end{array}\right) : \framep[n-1][n-1]\rightarrow Type_l
            }                                                            \\
            \painting[n][n]              &
            \left(\begin{array}{l}
                      \framep[n-1][0,...,n-1]   \\
                      \painting[n-1][0,...,n-1] \\
                      \star                     \\
                      \star                     \\
                      \restrp[n][0,...,n-1]     \\
                      \star                     \\
                      E                         \\
                    \end{array}\right) & \defeq & E                        \\
            \painting[n][p](p<n)         &
            \left(\begin{array}{l}
                      \framep[n-1][0,...,p-1]   \\
                      \painting[n-1][0,...,p-1] \\
                      \framep[n-1][p,...,n-1]   \\
                      \painting[n-1][p,...,n-1] \\
                      \restrf[n][0,...,p-1]     \\
                      \restrf[n][p,...,n-1]     \\
                      E                         \\
                    \end{array}\right) & \defeq & d \mapsto
            \left(\begin{array}{l}
                      \Sigma l:(\Pi q\leq n.\,\Pi \omega.\
                      \painting[n-1][0,...,p](\restrf[n][p](d))). \\
                      \painting[n][p+1,...,n-1]
                      \left(\begin{array}{l}
                          \framep[n-1][0,...,p]       \\
                          \painting[n-1][0,...,p]     \\
                          \framep[n-1][p+1,...,n-1]   \\
                          \painting[n-1][p+1,...,n-1] \\
                          \restrf[n][0,...,p]         \\
                          \restrf[n][p+1,...,n-1]     \\
                          E                           \\
                        \end{array}\right)(d,l)           \\
                    \end{array}\right) \\
          \end{array}
        $$

@@
